---
title: "DataAnalysisBackend"
author: "Richie Fleming"
date: "2024-05-23"
output: html_document
---

```{r}
data = read.csv("C:\\Users\\rflem\\OneDrive\\Desktop\\Projects Summer 24\\AttemptRoom\\Roommate_Matching_Simulated_Data_Updated.csv")
```

Note: that this data is not indicative of the real data. All data is simulated

```{r}
head(data)
keeps <- c("Days.Out", "Bedtime", "Wake.Up.Time", "Cleanliness", "GPA")
clean_data <- data[keeps]
head(clean_data)
```
Exploring Data:
Since we don't have a dependent variable, ie. Roommate satisfaction score, we will use GPA as a DV. (Based on the assumption that people with similar GPA will be more compatible)

Test different models using bidirectional approach of feature selection. (Start with limited model)

```{r}
null_model <- lm(GPA ~ 1, data = clean_data)
full_model <- lm(GPA ~ ., data =clean_data)


fwd_m <- step(null_model, direction = "forward", scope = list(lower = null_model, upper = full_model))

bwd_m <- step(full_model, direction = "backward", k = 2)


both_m <- step(null_model, direction = "both", scope = list(lower = null_model, upper = full_model), k = 2)
```
```{r}
aic_values <- c(Forward = AIC(fwd_m), Backward = AIC(bwd_m), Both = AIC(both_m))
aic_values
```

```{r}
summary(fwd_m)
summary(bwd_m)
summary(both_m)
summary(null_model)
```
```{r}
plot(fwd_m)
```
Based on the data we collected, we can't accurately predict GPA based on the features we selected. 
Our R_squared values are significantly below 0.5, meaning we are performing worse than the mean. Also with a p-value of < alpha/2 we can be confident in the significance of this value. 
- Exclude GPA from our survey questions. 


Conclusion: 
Using a linear model may not be the best approach: Switch to Cosine similarity using a vector of 10 values from survey questions. 
